\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Rohan Rajpal}

\section{Work experience}

\begin{eventlist}
    
\item{May 2018 -- July 2018}
     {\href{https://realvol.in/}{Realvol}, Delhi, India}
     {Software Developer}

    I worked on the mobile VR application. We worked with the Unity Game Engine which involves making game objects and C sharp scripts.

\item{July 2017 - May 2018}
     {Women Who Code, Delhi}
     {Social Media Manager}
     
      I worked on increasing the outreach of WWCD. Informing people on social media about events and talking to recruits.
      
      
\section{Projects}
\item{February 2019}
    {IIITD}
    {Movie Recommender System}
    
    I made a movie recommender system.This project involved implementing collaborating filtering techniques to recommend movies. It also involved database management using MongoDB, making dynamic web applications with Flask, HTML and deploying web apps to Heroku and Docker.

\item{October 2018 - November 2018}
    {IIITD}
    {\href{https://docs.google.com/presentation/d/1kuuXjSpsZCvphLWA3AERzbiuz_m70CpEDbWSMaA2VZU/edit?usp=sharing}{Game: Snake Vs Block}}
    
    We had a group project to make a replica of the game Snake Vs Block. I worked on the collision, animations, UI and UX. The game was built on Java using JavaFX. All the code is available on GitHub.
    
\item{October 2018 - November 2018}
    {IIITD}
    {Share My Space}
    
    The project allowed two people in different places to communicate via VR. The major work in it involved morphing two rooms into one. I worked on providing the room layouts and helping to set them up in Unity. I also got acquainted with LEAP Motion, Microsoft Kinect and HTC Vive while working on the project.
    
\item{June 2018}
    {Sunrise Polymold}
    {\href{https://youtu.be/mjULJuEKHKk}{ERP System for a Factory}}
    
    I made an android app which was used to carry out the operations in a factory. The database handling was done using Firebase. I used the real-time database to store all data.

    
\item{January 2018 - May 2018}
     {IIITD}
     {\href{https://youtu.be/4MwRjWmVerA}{Smart Vehicle Management System}}

My team and I had created a retractable speed breaker that would help in reducing traffic congestion. I handled the hardware(Arduino) and design role in the whole project.

\personal
    [github.com/rohanrajpal]
    {Gurgaon}
    {+91 9871739342}
    {rohan17089@iiitd.ac.in}
    {linkedin.com/in/rohanrajpal/}
    {codechef.com/users/rohanrajpal}
    
    
\section{Activities}
\item
    {}
    {Contributions}
    {Open Source}
    
    I've created patches that have been accepted in humongous organisations like \href{https://bugzilla.mozilla.org/show_bug.cgi?id=1422035}{Mozilla}, \href{https://trac.videolan.org/vlc/ticket/21952}{VLC} and \href{https://github.com/coala/documentation/pull/590}{Coala}.
    
\item{January 2019 - Present}
    {Google}
    {Lead, Developer Student Club}
    
    Google collaborates with university students who are passionate about growing developer communities and supports them with starting student clubs on their campuses.
    
\item
    {2018}
    {Game Design Hackathon}
    {\href{https://rohanrajpal.itch.io/need-my-space}{Secured 9th Position}}
    
    My team and I made an endless runner game. We used Unity Game Engine to build the game and the coding part was done using C sharp scripts.
    
    
\item{2018}
     {Odyssey '18}
     {Organising Team}

I was a part of the sponsorship team, we approached different companies and made deals with them to be sponsors for our events.
The work helped me in improving my networking skills.

\item
{2017}
    {Organising Team}
    {Vistara Hackathon}
    
    I compered for the event and helped in organising as well.
    
\end{eventlist}


\section{Education}

\begin{yearlist}

\item[Undergraduate]{2017 -- present }
     {B.TECH IN COMPUTER SCIENCE
AND ENGINEERING }
     {Indraprastha Institute of Information Technology, Delhi
     CGPA: 8.87}

\item{2015 -- 2017}
     {Delhi Public School, Vasant Kunj}
     {Gold Medal for proficiency in academics for seven consecutive years.}

\end{yearlist}

\section{Software skills}

\begin{factlist}

\item{Languages}
     {C++, C, C Sharp, Java, HTML, Python, CSS, Verilog, bash
       \LaTeX}

\item{Tools}
     {MySQL, Django, Flask, Linux, Firebase,Unity, Git, Mercurial, Shell, JavaFX, Leap Motion, Kinect, HTC Vive}


\end{factlist}
\section{Courses}
\begin{factlist}
\item{Operating Systems}{}
\item{Database Management Systems}{}
\item{Analysis and Design of Algorithms}{}

\item{Advance Programming}{}
\item{Introduction to Engineering and Design}{}
\item{Discrete Mathematics}{}
\item{Data Structures and Algorithms}{}

\end{factlist}

\section{School Projects}

\begin{yearlist}

\item{2015}
     {Google Science Fair (\href{https://www.googlesciencefair.com/projects/en/2015/01ce2a5097227cd2bf078607d16fc07fb6949b23961a011cd0bda6d0c2fb011a}{Project})}
     {Energy Generation System}

\item{2014}
     {Custom ROM (\href{https://forum.xda-developers.com/showthread.php?t=2756571}{xdadevelopers})}
     {Compiled a custom ROM for my phone}


\end{yearlist}


\end{document}
